Direction-aware functional class scoring enrichment analysis of Infinium DNA methylation data

### 2024-01-25 manuscript/manuscript.Rmd
heading levels

## Abstract

@@

## Introduction

@@

## Methods

### Implementation overview

@@

### Method validation using simulations

@@

### Sensitivity analysis

@@

### Association of methylation with gene expression

@@

### Pathway-level differential methylation in aging

@@

### Pathway-level differential methylation in assisted reproductive technology

@@

### Differential pathway methylation in 19 common disease states

@@

## Results

### Evaluation of FCS methods for Infinium methylation array data

@@

### Sensitivity of GSA and LAM methods with real cancer data

@@

## Discussion

@@

## Bibliography

>>>>

# Abstract

@@

# Introduction

@@

# Methods

## Implementation overview

@@

## Method validation using simulations

@@

## Sensitivity analysis

@@

## Association of methylation with gene expression

@@

## Pathway-level differential methylation in aging

@@

## Pathway-level differential methylation in assisted reproductive technology

@@

@@

# Results

## Evaluation of FCS methods for Infinium methylation array data

@@

## Sensitivity of GSA and LAM methods with real cancer data

@@

# Discussion

@@

# Bibliography
